Definition of Archipelagos

### 2025-01-15 application_examples/abc_inferences/archipelago-definition.Rmd
Updating last changes to be able to pull

>>>>

```{r}
gtf_df[gtf_df$seqnames=="NC_036801.1" & gtf_df$type == "gene",]
gtf_df[gtf_df$gene_id == "LOC101483164",]
```

```{r}
dpp4_chr <- "NC_036801.1"
dpp4_start <- 29502362
dpp4_end <- 29517382
gtf_df[gtf_df$seqnames=="NC_036801.1" & gtf_df$type == "gene" & gtf_df$start > dpp4_start - 5e5 & gtf_df$end > dpp4_end + 5e5  ,]
```
